---
title: "eds221-1-1-not-in-analysis"
format: html
editor: visual
---

## 

## EDS 221 Day 1

```{r}
library(tidyverse)
```

practicing making file paths

## Read in data

```{r}
energy <- read_csv("data/us_energy.csv")
energy
```

create a line chart of energy over time, with color based on the energy type.

(we don't need to group by type if we have another grouping factor like mapping a color aesthetic = type.)

```{r}
ggplot(data = energy, aes(x = year, y = quadrillion_btu
                        #  , group = type
                          )) +
  geom_line(aes(color = type)) +
  geom_point(aes(color = type)) +
  theme_minimal()
```

where we place the data, aes(x = variable, y = variable) matters. if we want to have different layers referring to SAME variables, put in ggplot(). if different layers have diff variables, put in each layer (geom_point(), geom_line(), etc.)

```{r}
ggplot() +
  geom_point(data = energy, aes(x = year, y = quadrillion_btu, color = type)) +
  geom_line(data = energy, aes(x = year, y = quadrillion_btu, color = type)) + 
  theme_minimal()
```
